---
title: "Handling Missingness and Non-Convergence in Simulation Studies"
subtitle: "Randomizing papers for agreement assessment"
author: 
 - Samuel Pawel
 - Björn S. Siepe
 - Anna Lohmann
 - František Bartoš
date: "15 August 2024"
format:
  html:
    toc: true
    number-sections: true
    theme: cosmo
    code-fold: true
    code-tools: true
    code-summary: "Show the code"
    fig-width: 7
    fig-height: 4.5
execute:
  message: false
  warning: false
---

# Background
This document contains code to randomize papers from the literature review to assess agreement between different raters.

# Prep

Load the data and the tidyverse packages: 
```{r}
set.seed(2024)
library(tidyverse)
library(readxl)

# Load the data
data_fb <- read_xlsx("data/lit_review_data_FB.xlsx")
data_sp <- read_xlsx("data/lit_review_data_SP.xlsx")
data_al <- read_xlsx("data/lit_review_data_AL.xlsx")
data_bs <- read_xlsx("data/lit_review_data_BS.xlsx")

```

Combine data sets: 
```{r}
data_review <- rbind(data_fb, data_sp, data_al, data_bs)

# delete all rows without doi
data_review <- data_review[!is.na(data_review$doi), ]
```




# Randomize papers

As we preregistered:

> Fifty studies will be coded in duplicate by a second coder. We will start with the studies that have received the lowest confidence rating (and randomly break ties). 

```{r}
# Names of coders
coders <- unique(data_review$reviewer)

# start with low certainty
low_cert <- data_review[data_review$Q7_coding_confidence == "low", ]

# Step 2: Check if the number of "low" certainty rows is less than 50
if (nrow(low_cert) < 50) {
  # Step 3: If less than 50, get additional rows with "medium" certainty
  rows_needed <- 50 - nrow(low_cert)
  medium_cert <- data_review[data_review$Q7_coding_confidence == "medium", ]
  
  # Step 4: Randomly sample the required number of "medium" certainty rows
  add_sample <- medium_cert[sample(1:nrow(medium_cert), rows_needed), ]
  
  # Step 5: Combine the "low" certainty rows with the sampled "medium" certainty rows
  final_sample <- rbind(low_cert, add_sample)
} else {
  # if there are 50 or more "low" certainty rows
  final_sample <- low_cert[sample(1:nrow(low_cert), 50), ]
}

# randomize the new coder in a new column
final_sample$new_coder <- sapply(final_sample$reviewer, function(x) {
   sample(setdiff(coders, x), 1)
})
```

Check the number of papers each coder has to code:
```{r}
final_sample %>%
  group_by(reviewer) %>%
  summarise(n = n())
```

Create a list of DOIs for each individual coder:
```{r}
final_sample %>%
  group_by(reviewer) %>%
  summarise(dois = paste(doi, collapse = ", "))
```


