---
title: "miss-sim"
subtitle: "Randomizing papers for agreement assessment"
author: "Björn S. Siepe"
date: "15 August 2024"
format:
  html:
    toc: true
    number-sections: true
    theme: cosmo
    code-fold: true
    code-tools: true
    code-summary: "Show the code"
    fig-width: 7
    fig-height: 4.5
execute:
  message: false
  warning: false
---

# Background
This document contains code to randomize papers from the literature review to assess agreement between different raters

# Prep

Load the data and the tidyverse packages: 
```{r}
set.seed(2024)
library(tidyverse)

# Load the data


```


# Randomize papers

As we preregistered:

> Fifty studies will be coded in duplicate by a second coder. We will start with the studies that have received the lowest confidence rating (and randomly break ties). 

```{r}
# with made-up data for now
df <- data.frame(
  reviewer = sample(c("AL", "SP", "FB", "BS"), 200, replace = TRUE),
  # generate mock dois
  doi = paste0("10.1234/", sample(letters, 200, replace = TRUE), sample(letters, 200, replace = TRUE), sample(letters, 200, replace = TRUE)),
  Q7_coding_confidence = sample(c("low", "medium", "high"), 200, replace = TRUE)
)
coders <- unique(df$reviewer)

# start with low certainty
low_cert <- df[df$Q7_coding_confidence == "low", ]

# Step 2: Check if the number of "low" certainty rows is less than 50
if (nrow(low_cert) < 50) {
  # Step 3: If less than 50, get additional rows with "medium" certainty
  rows_needed <- 50 - nrow(low_cert)
  medium_cert <- df[df$Q7_coding_confidence == "medium", ]
  
  # Step 4: Randomly sample the required number of "medium" certainty rows
  add_sample <- medium_cert[sample(1:nrow(medium_cert), rows_needed), ]
  
  # Step 5: Combine the "low" certainty rows with the sampled "medium" certainty rows
  final_sample <- rbind(low_cert, add_sample)
} else {
  # if there are 50 or more "low" certainty rows
  final_sample <- low_cert[sample(1:nrow(low_cert), 50), ]
}

# randomize the new coder in a new column
final_sample$new_coder <- sapply(final_sample$reviewer, function(x) {
   sample(setdiff(coders, x), 1)
})
```

Check the number of papers each coder has to code:
```{r}
final_sample %>%
  group_by(reviewer) %>%
  summarise(n = n())
```

Create a list of DOIs for each individual coder:
```{r}
final_sample %>%
  group_by(reviewer) %>%
  summarise(dois = paste(doi, collapse = ", "))
```


